---
title: "Thesis Simulation"
author: "Jack Yoon"
output:
  pdf_document:
    toc: true
    number_sections: true
toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

\newpage

\section{Data and Libraries}

```{r,cache=T}
#Load Libraries 
library(quantmod)
library(ggplot2)
library(coda)

#Use Quantmod to get data from 2000 to 2021
getSymbols("SPY",
           from = "2000/01/07",
           to = "2021/12/31",
           periodicity = "daily")
getSymbols("^VIX",
           from = "2000/01/07",
           to = "2021/12/31",
           periodicity = "daily")

#Create a merged data table of SPY, VIX data
total = data.frame(merge(VIX,SPY))

#Calculate daily changes in dividend/split-adjusted SPY values
total$return.daily.adjust = rep(NA,nrow(total))
for(i in 2:nrow(total)){
  total$return.daily.adjust[i] = total$SPY.Adjusted[i]/total$SPY.Adjusted[i-1]-1
}
```

\newpage

\section{Simulation: Block Resampling with Time Dependence}

```{r,cache=T}
set.seed(98)

#Initial conditions
ndays = c(252*12)
ntimelines = 100
block.size = 15
block.num = floor(ndays/block.size)
otm = 0.6 #OTM degree
equity.perc = 0.92
option.perc = 0.08

#Upper and lower bounds for the VIX during conditional resampling of S&P500 (SPY) value
lambda = c(1)

#Final list of results
returns.final = list()
vix.final = list()
invest.final = list()

#Black-Scholes algorithm (https://financetrain.com/black-scholes-options-pricing-model-in-r)
bs <- function(S, K, r, T, sig, type){
  
  if(type=="C"){
    d1 <- (log(S/K) + (r + sig^2/2)*T) / (sig*sqrt(T))
    d2 <- d1 - sig*sqrt(T)
    
    value <- S*pnorm(d1) - K*exp(-r*T)*pnorm(d2)
    return(value)
  }
  
  if(type=="P"){
    d1 <- (log(S/K) + (r + sig^2/2)*T) / (sig*sqrt(T))
    d2 <- d1 - sig*sqrt(T)
    
    value <-  (K*exp(-r*T)*pnorm(-d2) - S*pnorm(-d1))
    return(value)
  }
}

#Vary the number of trading days, ndays
for(n in 1:length(ndays)){
  
  #Vary the bound, lambda, of VIX values on which conditional resampling is based
  for(l in 1:length(lambda)){
    
    #Create result matrices to store data
    results.returns = matrix(NA,nrow=ndays[n],ncol=ntimelines)
    results.vix = matrix(NA,nrow=ndays[n],ncol=ntimelines)
    results.options = matrix(NA,nrow=ndays[n],ncol=ntimelines)
    results.invest = matrix(NA,nrow=ndays[n]+1,ncol=ntimelines)
    
    #Begin looping through different "timelines"
    for(t in 1:ntimelines){
      
      #Create empty vectors to store return and VIX values
      return.vals = rep(NA,ndays[n])
      vix.vals = rep(NA,ndays[n])
      invest.vals = rep(NA,ndays[n]+1)
  
      #Sample an initial starting index
      index.initial = sample(length(total$VIX.Close)-block.size,1)
      vix.vals[1:(block.size)] = total$VIX.Close[(index.initial):(index.initial+block.size-1)]
      
      #Calculate all daily VIX values based on block resampling
      for(i in 2:block.num[n]){
        
        #Set bounds for VIX values
        vix.lower = vix.vals[(block.size*(i-1))]-lambda[l]
        vix.upper = vix.vals[(block.size*(i-1))]+lambda[l]
        
        #Next day VIX values corresponding to these values
        currentday.index = which(total$VIX.Close[1:(length(total$VIX.Close)-block.size)] > vix.lower & total$VIX.Close[1:(length(total$VIX.Close)-block.size)] < vix.upper)
        nextday.index = currentday.index+1
        
        #Sample an index value from the list of next day indices
        nextblock.index = nextday.index[sample(length(nextday.index),1)]
        
        #Fill in values for a particular block by referring to the historical VIX data
        vix.vals[((i-1)*block.size+1):((i-1)*block.size+block.size)] = total$VIX.Close[(nextblock.index):(nextblock.index+block.size-1)]
        
        #For situations where ndays aren't perfectly divisible by block size
        if(i == block.num[n] & is.na(vix.vals[length(vix.vals)])){
          
          #Calculate values left to fill
          vals.left = sum(is.na(vix.vals[length(vix.vals)]))
          
          #Sample an initial starting index
          index.initial = sample(length(total$VIX.Close)-block.size,1)
          
          #Fill in remaining values for the VIX 
          vix.vals[((i)*block.size+1):length(vix.vals)] = total$VIX.Close[(index.initial):(index.initial+vals.left-1)]
        }
        
      }
      
      #Set lower and upper bounds for the VIX
      lower.vix = vix.vals[1]-lambda[l]
      upper.vix = vix.vals[1]+lambda[l]
      
      #Specify for which day indices the VIX was between lower and upper bounds
      indices = which(total$VIX.Close > lower.vix & total$VIX.Close < upper.vix)
        
      #Sample a return value from the conditional distribution of SPY for a particular value of VIX
      return.vals[1] = total$return.daily.adjust[indices[sample(length(indices),1)]]
      
      #Calculate daily stock return values by performing conditional resampling, based on VIX values on particular days
      for(i in 2:length(vix.vals)){
        
        #Set lower and upper bounds for the VIX
        lower.vix = vix.vals[i]-lambda[l]
        upper.vix = vix.vals[i]+lambda[l]
        
        #Specify for which day indices the VIX was between lower and upper bounds
        indices = which(total$VIX.Close > lower.vix & total$VIX.Close < upper.vix)
        
        #Next day values
        next.indices = indices+1
        
        #Check if these don't go out of index range
        if(max(next.indices)>length(total$return.daily.adjust)){
          next.indices = next.indices[1:(length(next.indices)-1)]
        }
        
        #Sample a return value from the conditional distribution of SPY for a particular value of VIX
        return.vals[i] = total$return.daily.adjust[next.indices[sample(length(next.indices),1)]]
        
      }
    
      #Plug in the returns and VIX values from a particular timeline (t) into a column of the results matrix
      results.returns[,t] = return.vals
      results.vix[,t] = vix.vals
    
      #Calculate returns for a standard $1000 investment
      invest.vals[1] = 1000
      
      for(d in 1:ndays[n]){
        invest.vals[d+1] = invest.vals[d]*(1+results.returns[d,t])
        
        if(invest.vals[d+1]==0){
          break
        }
      }
      
      #Now we have a list of S&P500 index levels and corresponding VIX levels
      total.portval2 = rep(NA,ndays[n]-1)
      total.portval2[1] = 1000
      equity.portval = total.portval2[1]*equity.perc
      option.portval = total.portval2[1]*option.perc
      temp.option.budget = option.portval
      num.contract = 0
      price.contract = 0
      protection = 0
      profit = 0
      vix.lower = 20
      vix.upper = 70
      mark.day = 1
      
      for(d in 2:ndays[n]){
        equity.portval = equity.portval*invest.vals[d]/invest.vals[d-1]
        
        if(vix.vals[d] < 20 & protection == 0 & temp.option.budget > 0){
          #Take on protection (calculate option price for 60% OTM)
          price.contract = bs(invest.vals[d],invest.vals[d]*(1-otm),0.0217,2,vix.vals[d]/100,"P")
          mark.day = d
          
          #Take this offer price; build in a liquidity premium (liq.prem)
          num.contract = floor(temp.option.budget/price.contract)
          
          #Switch protection on
          protection = 1
        }
        
        #Having taken on protection, we need to watch out for selling opportunities (earlier of 2*VIX Std. Dev movement or end of year rebalancing)
        if(vix.vals[d] > vix.upper & protection == 1 & temp.option.budget > 0 & d-mark.day < 252*2){
          #How far are we from the mark.day? (if we're above 365, then we need to cut prematurely)
          price.sale = bs(invest.vals[d],invest.vals[mark.day]*(1-otm),0.0217,(d-mark.day)/252,vix.vals[d]/100,"P")
          
          #Look up price on the sell date
          profit = (price.sale-price.contract)*num.contract + profit
          temp.option.budget = temp.option.budget + profit
          
          total.portval = equity.portval + temp.option.budget
          equity.portval = total.portval*equity.perc
          option.portval = total.portval*option.perc
          temp.option.budget = option.portval
          
          #Switch off protection
          protection = 0
          profit = 0
        }
        
        #Watch out for the end of the year
        if(d-mark.day == 252*2 & protection == 1 & temp.option.budget > 0){
          #Find the price of the option contract on this particular day, or nearest to the day
          price.sale = bs(invest.vals[d],invest.vals[mark.day]*(1-otm),0.0217,0,vix.vals[d]/100,"P")
          
          #Look up price on the sell date
          profit = (price.sale-price.contract)*num.contract + profit
          temp.option.budget = temp.option.budget + profit
          
          total.portval = equity.portval + temp.option.budget
          equity.portval = total.portval*equity.perc
          option.portval = total.portval*option.perc
          temp.option.budget = option.portval
          
          #Switch off protection
          protection = 0
          profit = 0
        }
        
        total.portval2[d] = equity.portval + option.portval
      }
      
      
      #Plug in return values for $1000 investment from a particular timeline (t) into a column of the final results matrix, results.invest
      results.invest[,t] = invest.vals
      results.options[,t] = total.portval2
    }
    
    #Append result matrices to list of final results
    returns.final[[((which(ndays == ndays[n])-1)*length(lambda)+which(lambda == lambda[l]))]] = results.returns
    
    vix.final[[((which(ndays == ndays[n])-1)*length(lambda)+which(lambda == lambda[l]))]] = results.vix
    
    invest.final[[((which(ndays == ndays[n])-1)*length(lambda)+which(lambda == lambda[l]))]] = results.invest
    
    #Rename list elements
    names(returns.final)[((which(ndays == ndays[n])-1)*length(lambda)+which(lambda == lambda[l]))] = paste(ndays[n]," trading days and ",lambda[l]," bounds")
    
    names(vix.final)[((which(ndays == ndays[n])-1)*length(lambda)+which(lambda == lambda[l]))] = paste(ndays[n]," trading days and ",lambda[l]," bounds")
    
    names(invest.final)[((which(ndays == ndays[n])-1)*length(lambda)+which(lambda == lambda[l]))] = paste(ndays[n]," trading days and ",lambda[l]," bounds")
    
  }
}
```

```{r}
#Calculate 10-Year CAGR for each simulation
cagr.index = rep(NA,100)
cagr.options = rep(NA,100)
for(i in 1:100){
  cagr.index[i] = (results.invest[,i][252*5]/results.invest[,i][1])^(1/5)-1
  cagr.options[i] = (results.options[,i][252*5]/results.options[,i][1])^(1/5)-1
}

tenyear.options.sim = quantile(cagr.options)
tenyear.index.sim = quantile(cagr.index)
tenyear.diff.sim = quantile(cagr.options)-quantile(cagr.index)

fiveyear.options.sim = quantile(cagr.options)
fiveyear.index.sim = quantile(cagr.index)
fiveyear.diff.sim = quantile(cagr.options)-quantile(cagr.index)


plot(results.options[,30],type="l",main="The Source of Extraordinary Returns: High-Vol Scenarios",xlab="Time",ylab="Portfolio Value (Initial = $1,000)")
par(new = TRUE)                             # Add new plot
plot(results.vix[,30], type="l", col = "red",              # Create second plot without axes
     axes = FALSE, xlab = "",ylab=" ")
axis(side = 4, at = pretty(range(results.vix)))      # Add second axis
mtext("y2", side = 4, line = 3)

```

\subsection{Results}

\subsubsection{Similarity to True S\&P500 and VIX}

**Distribution**

```{r,warning=F,cache=T}
### KS Tests

#Calculate p-values for KS tests of simulated S&P500 data
temp = rep(NA,length(returns.final))
pval=list()
for(i in 1:length(returns.final)){
  pval[[i]]=rep(NA,dim(returns.final[[i]])[2])
  for(j in 1:dim(returns.final[[i]])[2]){
    pval[[i]][j]=ks.test(returns.final[[i]][,j],total$return.daily.adjust)$p.value
  }
  temp[i] = mean(pval[[i]])
}

#Results matrix
pvals = matrix(temp,nrow=length(ndays),ncol=length(lambda),byrow=T)
rownames(pvals) = c("10 Years","15 Years","20 Years","27 Years")
colnames(pvals) = c("Bound = 1","Bound = 3","Bound = 7","Bound = 10")
pvals

#Calculate p-values for KS tests of simulated S&P500 data
temp = rep(NA,length(vix.final))
pval=list()
for(i in 1:length(vix.final)){
  pval[[i]]=rep(NA,dim(vix.final[[i]])[2])
  for(j in 1:dim(vix.final[[i]])[2]){
    pval[[i]][j]=ks.test(vix.final[[i]][,j],total$VIX.Close)$p.value
  }
  temp[i] = mean(pval[[i]])
}

#Results matrix
pvals = matrix(temp,nrow=length(ndays),ncol=length(lambda),byrow=T)
rownames(pvals) = c("10 Years","15 Years","20 Years","27 Years")
colnames(pvals) = c("Bound = 1","Bound = 3","Bound = 7","Bound = 10")
pvals

### QQ Plots

#Key for reading the QQ Plot graph labels: scenario "i" corresponds to the following conditions
key = matrix(rep(1:16),nrow=length(ndays),ncol=length(lambda),byrow=T)
rownames(key) = c("10 Years","15 Years","20 Years","27 Years")
colnames(key) = c("Bound = 1","Bound = 3","Bound = 7","Bound = 10")
key

#Plot QQ plots for simulated S&P500 data
conditions = sample(length(returns.final),2,replace=F)
simulations = sample(dim(returns.final[[i]])[2],2,replace=F)
for(i in conditions){
  for(j in simulations){
    qqplot(total$return.daily.adjust,returns.final[[i]][,j],xlab="Historical Returns",ylab="Simulated Returns",main=paste("Method 1 QQ Plot Scenario",i,"Simulation",j))
  }
}

#Plot QQ plots for simulated VIX data
qqplot(total$VIX.Close,vix.final[[13]][,77],xlab="Historical VIX",ylab="Simulated VIX",main=paste("Method 1 QQ Plot Scenario",13,"Simulation",77))
qqplot(total$VIX.Close,vix.final[[16]][,77],xlab="Historical VIX",ylab="Simulated VIX",main=paste("Method 1 QQ Plot Scenario",16,"Simulation",77))
```

We can perform this in comparison with a smaller time period as well.

```{r,warning=F,cache=T}
### KS Tests

#Calculate p-values for KS tests of simulated S&P500 data
temp = rep(NA,length(returns.final))
pval=list()
for(i in 1:length(returns.final)){
  pval[[i]]=rep(NA,dim(returns.final[[i]])[2])
  for(j in 1:dim(returns.final[[i]])[2]){
    pval[[i]][j]=ks.test(returns.final[[i]][,j],total$return.daily.adjust[2:1500])$p.value
  }
  temp[i] = mean(pval[[i]])
}

#Results matrix
pvals = matrix(temp,nrow=length(ndays),ncol=length(lambda),byrow=T)
rownames(pvals) = c("10 Years","15 Years","20 Years","27 Years")
colnames(pvals) = c("Bound = 1","Bound = 3","Bound = 7","Bound = 10")
pvals

#Calculate p-values for KS tests of simulated VIX data
temp = rep(NA,length(vix.final))
pval=list()
for(i in 1:length(vix.final)){
  pval[[i]]=rep(NA,dim(vix.final[[i]])[2])
  for(j in 1:dim(vix.final[[i]])[2]){
    pval[[i]][j]=ks.test(vix.final[[i]][,j],total$VIX.Close[2:1500])$p.value
  }
  temp[i] = mean(pval[[i]])
}

#Results matrix
pvals = matrix(temp,nrow=length(ndays),ncol=length(lambda),byrow=T)
rownames(pvals) = c("10 Years","15 Years","20 Years","27 Years")
colnames(pvals) = c("Bound = 1","Bound = 3","Bound = 7","Bound = 10")
pvals

### QQ Plots

#Key for reading the QQ Plot graph labels: scenario "i" corresponds to the following conditions
key = matrix(rep(1:16),nrow=length(ndays),ncol=length(lambda),byrow=T)
rownames(key) = c("10 Years","15 Years","20 Years","27 Years")
colnames(key) = c("Bound = 1","Bound = 3","Bound = 7","Bound = 10")
key

#Plot QQ plots for simulated S&P500 data
qqplot(total$return.daily.adjust[2:1500],returns.final[[13]][,77],xlab="Historical Returns",ylab="Simulated Returns",main=paste("Method 1 QQ Plot Scenario",13,"Simulation",77))
qqplot(total$return.daily.adjust[2:1500],returns.final[[16]][,77],xlab="Historical Returns",ylab="Simulated Returns",main=paste("Method 1 QQ Plot Scenario",16,"Simulation",77))

#Plot QQ plots for simulated VIX data
qqplot(total$VIX.Close[2:3000],vix.final[[13]][,77],xlab="Historical VIX",ylab="Simulated VIX",main=paste("Method 1 QQ Plot Scenario",13,"Simulation",77))
qqplot(total$VIX.Close[2:3000],vix.final[[16]][,77],xlab="Historical VIX",ylab="Simulated VIX",main=paste("Method 1 QQ Plot Scenario",16,"Simulation",77))
```

**ACF**

```{r,cache=T}
###Create daily and monthly autocorrelation plots for the S&P 500

#Daily ACF (index vals from 2:length because the first value is NA)
acf(total$return.daily.adjust[2:length(total$return.daily.adjust)],main="Daily S&P500 Autocorrelation Plot, 2000-2021")

#Monthly ACF
limit = floor(length(total$return.daily.adjust)/30)
month.index = 30*(1:limit)
acf(total$return.daily.adjust[month.index],main="Monthly S&P500 Autocorrelation Plot, 2000-2021")

#Quarterly ACF
limit = floor(length(total$return.daily.adjust)/90)
season.index = 90*(1:limit)
acf(total$return.daily.adjust[season.index],main="Quarterly S&P500 Autocorrelation Plot, 2000-2021")

###Create daily and monthly autocorrelation plots for simulated data

#Key for reading the ACF plot labels: scenario "i" corresponds to the following conditions
key = matrix(rep(1:16),nrow=length(ndays),ncol=length(lambda),byrow=T)
rownames(key) = c("10 Years","15 Years","20 Years","27 Years")
colnames(key) = c("Bound = 1","Bound = 3","Bound = 7","Bound = 10")
key

#Daily ACF
conditions = sample(length(returns.final),2,replace=F)
simulations = sample(dim(returns.final[[i]])[2],2,replace=F)
for(i in conditions){
  for(j in simulations){
    acf(returns.final[[i]][,j],main=paste("Method 1 Daily Returns ACF Scenario",i,"Simulation",j))
  }
}

#Monthly ACF
conditions = sample(length(returns.final),2,replace=F)
simulations = sample(dim(returns.final[[i]])[2],2,replace=F)
for(i in conditions){
  for(j in simulations){
    limit = floor(length(returns.final[[i]][,j])/30)
    month.index = 30*(1:limit)
    acf(returns.final[[i]][,j][month.index],main=paste("Method 1 Monthly Returns ACF Scenario",i,"Simulation",j))
  }
}

#Quarterly ACF
conditions = sample(length(returns.final),2,replace=F)
simulations = sample(dim(returns.final[[i]])[2],2,replace=F)
for(i in conditions){
  for(j in simulations){
    limit = floor(length(returns.final[[i]][,j])/90)
    season.index = 90*(1:limit)
    acf(returns.final[[i]][,j][season.index],main=paste("Method 1 Quarterly Returns ACF Scenario",i,"Simulation",j))
  }
}
```

We perform the same analysis for VIX data.

```{r,cache=T}
###Create daily and monthly autocorrelation plots for the VIX

#Daily ACF
acf(total$VIX.Close,main="Daily VIX Autocorrelation Plot, 2000-2021")

#Monthly ACF
limit = floor(length(total$VIX.Close)/30)
month.index = 30*(1:limit)
acf(total$VIX.Close[month.index],main="Monthly VIX Autocorrelation Plot, 2000-2021")

###Create daily and monthly autocorrelation plots for simulated data

#Key for reading the ACF plot labels: scenario "i" corresponds to the following conditions
key = matrix(rep(1:16),nrow=length(ndays),ncol=length(lambda),byrow=T)
rownames(key) = c("10 Years","15 Years","20 Years","27 Years")
colnames(key) = c("Bound = 1","Bound = 3","Bound = 7","Bound = 10")
key

#Daily ACF
acf(vix.final[[13]][,1],main=paste("Method 1 Daily VIX ACF Scenario",13,"Simulation",1))
acf(vix.final[[13]][,33],main=paste("Method 1 Daily VIX ACF Scenario",13,"Simulation",33))
acf(vix.final[[13]][,77],main=paste("Method 1 Daily VIX ACF Scenario",13,"Simulation",77))

#Monthly ACF
limit = floor(length(vix.final[[13]][,1])/30)
month.index = 30*(1:limit)
acf(vix.final[[13]][,1][month.index],main=paste("Method 1 Monthly VIX ACF Scenario",13,"Simulation",1))
acf(vix.final[[13]][,3][month.index],main=paste("Method 1 Monthly VIX ACF Scenario",13,"Simulation",33))
acf(vix.final[[13]][,5][month.index],main=paste("Method 1 Monthly VIX ACF Scenario",13,"Simulation",77))
```

**Volatility Clustering**

```{r,cache=T}
plot(returns.final[[13]][,77],xlab="Day Index",ylab="Returns",main=paste("Method 1 Volatility Clustering Scenario",13,"Simulation",77),type="l")
plot(returns.final[[16]][,77],xlab="Day Index",ylab="Returns",main=paste("Method 1 Volatility Clustering Scenario",16,"Simulation",77),type="l")


plot(vix.final[[13]][,77],returns.final[[13]][,77],xlab="VIX Index",ylab="Returns",main=paste("Method 1 Leverage Effect Scenario",13,"Simulation",77))
plot(vix.final[[16]][,77],returns.final[[16]][,77],xlab="VIX Index",ylab="Returns",main=paste("Method 1 Leverage Effect Scenario",16,"Simulation",77))
```

\subsubsection{Returns}

Calculation of returns for different conditions:

```{r,cache=T}
#Calculate CAGR Values
cagr = rep(NA,length(invest.final))
for(i in 1:length(invest.final)){
  cagr[i] = (mean(invest.final[[i]][nrow(invest.final[[i]]),])/1000)^(1/(nrow(invest.final[[i]])/253))-1
}

#Final Results
final.results = matrix(cagr,nrow=length(ndays),ncol=length(lambda),byrow=T)
rownames(final.results) = c("10 Years","15 Years","20 Years","27 Years")
colnames(final.results) = c("Bound = 1","Bound = 3","Bound = 7","Bound = 10")
final.results = round(final.results,3)
final.results*100

#Calculate CAGR Quantiles
cagr = list()
for(i in 1:length(invest.final)){
  cagr[[i]] = quantile(((invest.final[[i]][nrow(invest.final[[i]]),])/1000)^(1/(nrow(invest.final[[i]])/253))-1,c(0.025,0.975))
}
cagr
```

\subsubsection{Hypothesis Testing (P-Values)}

Calculation of p-values:

```{r,cache=T}
#Baseline CAGR
stocks = (total$SPY.Adjusted[length(total$SPY.Adjusted)]/total$SPY.Adjusted[1])^(1/27)-1
cagr.hist = 0.11

#Calculate P-Values
pvals = rep(NA,length(invest.final))
for(i in 1:length(invest.final)){
  x = (invest.final[[i]][nrow(invest.final[[i]]),]/1000)^(1/(nrow(invest.final[[i]])/253))-1
  pvals[i] = sum(x>cagr.hist)/length(x)
}

#Final Results
final.results = matrix(pvals,nrow=length(ndays),ncol=length(lambda),byrow=T)
rownames(final.results) = c("10 Years","15 Years","20 Years","27 Years")
colnames(final.results) = c("Bound = 1","Bound = 3","Bound = 7","Bound = 10")
final.results = round(final.results,3)
final.results
```

\subsubsection{Sampling Distribution Properties}

```{r,cache=T}
#Calculate All 100 CAGR Values for Scenario 13
cagr = rep(NA,100)
for(i in 1:100){
  cagr[i] = ((invest.final[[13]][nrow(invest.final[[13]]),i])/1000)^(1/(nrow(invest.final[[13]])/253))-1
}

#Summary Statistics, Histogram, and QQ Plot of CAGRs
summary(cagr)

boxplot(cagr,main="Boxplot of Returns, 27 Years w/ Lambda=1")

var(cagr)

hist(cagr,main="Histogram of CAGRs, Scenario 13",xlab="CAGR",breaks=40)

qqnorm(cagr,main="QQ Plot of CAGRs, Scenario 13",ylab="CAGR")
qqline(cagr,col="red")

ks.test(cagr,rnorm)$p.value


#Calculate All 100 CAGR Values for Scenario 1
cagr = rep(NA,100)
for(i in 1:100){
  cagr[i] = ((invest.final[[1]][nrow(invest.final[[1]]),i])/1000)^(1/(nrow(invest.final[[1]])/253))-1
}

#Summary Statistics, Histogram, QQ Plot, etc. of CAGRs
summary(cagr)

boxplot(cagr,main="Boxplot of Returns, 10 Years w/ Lambda=1")

var(cagr)

hist(cagr,main="Histogram of CAGRs, Scenario 1",xlab="CAGR",breaks=40)

qqnorm(cagr,main="QQ Plot of CAGRs, Scenario 1",ylab="CAGR")
qqline(cagr,col="red")

ks.test(cagr,rnorm)$p.value
```
