---
title: "Senior Thesis"
output: pdf_document
date: "2023-02-03"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#Read data
thesis.calls = read.csv("C:/Users/tyoon/Downloads/calloptions.csv")
thesis.puts = read.csv("C:/Users/tyoon/Downloads/putoptions.csv")
```

```{r}
#Extract YYYY, MM, DD from contract date and expiration date
thesis.calls$year.strike = substr(thesis.calls$date,1,4)
thesis.calls$month.strike = substr(thesis.calls$date,6,7)
thesis.calls$day.strike = substr(thesis.calls$date,9,10)

thesis.calls$year.exp = substr(thesis.calls$exdate,1,4)
thesis.calls$month.exp = substr(thesis.calls$exdate,6,7)
thesis.calls$day.exp = substr(thesis.calls$exdate,9,10)
```

```{r}
#Extract YYYY, MM, DD from contract date and expiration date
thesis.puts$year.strike = substr(thesis.puts$date,1,4)
thesis.puts$month.strike = substr(thesis.puts$date,5,6)
thesis.puts$day.strike = substr(thesis.puts$date,7,8)

thesis.puts$year.exp = substr(thesis.puts$exdate,1,4)
thesis.puts$month.exp = substr(thesis.puts$exdate,5,6)
thesis.puts$day.exp = substr(thesis.puts$exdate,7,8)
```

Extract long-dated European put options.

```{r}
#Create separate data files for long-dated put options which have annual expiry
##First, filter out the European put options
puts = thesis.puts[thesis.puts$cp_flag == "P" & thesis.puts$exercise_style == "E",]

##Convert dates into date class
puts$date = gsub(" ","",puts$date)
puts$date.strike = as.Date(puts$date, "%Y%m%d")

puts$exdate = gsub(" ","",puts$exdate)
puts$date.exp = as.Date(puts$exdate, "%Y%m%d")

puts$strike_price = as.numeric(puts$strike_price)/1000
```

```{r}
#Create separate data files for long-dated put options which have annual expiry
##First, filter out the European put options
calls = thesis.calls[thesis.calls$cp_flag == "C" & thesis.calls$exercise_style == "E",]

##Convert dates into date class
calls$date = gsub(" ","",calls$date)
calls$date.strike = as.Date(calls$date)

calls$exdate = gsub(" ","",calls$exdate)
calls$date.exp = as.Date(calls$exdate)

calls$strike_price = as.numeric(calls$strike_price)/1000
```

This block will help us get VIX, SPY data.

```{r,cache=T}
#Load Quantmod + Dependencies 
library(quantmod)

#Use Quantmod to get data from 1996 to 2021
getSymbols("SPY",
           from = "2000/01/07",
           to = "2021/12/31",
           periodicity = "daily")
getSymbols("^VIX",
           from = "2000/01/07",
           to = "2021/12/31",
           periodicity = "daily")

#Create a merged data table of SPY, VIX data
prices = data.frame(merge(VIX,SPY))

#Calculate daily changes in dividend/split-adjusted SPY values
prices$return.daily.adjust = rep(NA,nrow(prices))
for(i in 2:nrow(prices)){
  prices$return.daily.adjust[i] = prices$SPY.Adjusted[i]/prices$SPY.Adjusted[i-1]-1
}

#Date column
prices$date = rownames(prices)
```

Now, we can repeat this for all other years. Notice if there are any years in which you earn a positive return

```{r}
#Create a list with all separate yearly dataframes
#Puts
years = seq(2000,2021,1)
range = 22
puts.all = list()
for(i in 1:range){
  temp = puts[puts$year.strike == years[i],]
  puts.all[[i]] = temp
}
names(puts.all) = years

#Calls
years = seq(2000,2021,1)
range = 22
calls.all = list()
for(i in 1:range){
  temp = calls[calls$year.strike == years[i],]
  calls.all[[i]] = temp
}
names(calls.all) = years
```

Returns with fixed $1,000 budget and ideal option strike price determination based on VIX Units.

```{r}
#Go through each dataframe in the list and calculate abs.return, then record this return in a vector
returns = rep(NA,range)
budget = 1000
liq.prem = 1
vix.units = 0.25
for(i in 1:range){
  #Determine average offer price for puts sold on 1/4/96 and expiring on 12/21/96 for a strike price trading at 2 VIX Unit (%) below
  first.date = puts.all[[i]]$date.strike[1]
  first.date.options = puts.all[[i]][puts.all[[i]]$date.strike == first.date,]
  last.date = max(first.date.options$date.exp)
  
  first.weekday = as.integer(format(first.date,'%u'))
  last.weekday = as.integer(format(last.date,'%u'))
  
  first.date.equities = as.Date(ifelse(first.weekday >= 6, first.date + 5 - first.weekday, first.date))
  last.date.equities = as.Date(ifelse(last.weekday >= 6, last.date + 5 - last.weekday, last.date))
  
  spy.init = mean(prices$SPY.Open[prices$date == first.date.equities],prices$SPY.Close[prices$date == first.date.equities])*10
  vix.init = mean(prices$VIX.Open[prices$date == first.date],prices$VIX.Close[prices$date == first.date])
  strike.ideal = spy.init*(1-vix.init*vix.units/100)
  
  #Option Contract ID of the historical put option which traded closest to the ideal strike price for our transaction
  rownum = which.min(abs(puts.all[[i]]$strike_price[puts.all[[i]]$date.strike == first.date & puts.all[[i]]$date.exp == last.date] - strike.ideal))
  option.id = puts.all[[i]]$optionid[puts.all[[i]]$date.strike == first.date & puts.all[[i]]$date.exp == last.date][rownum]
  
  #Take this offer price; for now, pretend like there is unlimited liquidity for this particular contract (build in a liquidity premium for now, though)
  price.contract = puts.all[[i]]$best_offer[puts.all[[i]]$optionid == option.id & puts.all[[i]]$date.strike == first.date]*liq.prem
  num.contract = floor(budget/price.contract)
  
  #Now, find the average offer price for puts sold on the day closest to 12/21/96 at the same strike price
  contracts = puts.all[[i]][puts.all[[i]]$optionid == option.id & puts.all[[i]]$date.exp == last.date,]
  price.end = contracts$best_offer[dim(contracts)[1]]
  abs.return = (price.end-price.contract)*num.contract
  returns[i] = abs.return
}
```

Returns with fixed $1,000 budget and ideal option strike price determination based on fixed OTM percentage.

```{r}
#Version using OTM %
#Go through each dataframe in the list and calculate abs.return, then record this return in a vector
returns = rep(NA,range)
budget = 1000
liq.prem = 1 #1 means no liquidity premium
otm.perc = 0.1
for(i in 1:range){
  #Determine average offer price for puts sold on 1/4/96 and expiring on 12/21/96 for a strike price trading at OTM.perc (%) below
  first.date = puts.all[[i]]$date.strike[1]
  first.date.options = puts.all[[i]][puts.all[[i]]$date.strike == first.date,]
  last.date = max(first.date.options$date.exp)
  spy.init = mean(prices$SPY.Open[prices$date == first.date],prices$SPY.Close[prices$date == first.date])*10
  vix.init = mean(prices$VIX.Open[prices$date == first.date],prices$VIX.Close[prices$date == first.date])
  strike.ideal = spy.init*(1-otm.perc)
  
  #Option Contract ID of the historical put option which traded closest to the ideal strike price for our transaction
  rownum = which.min(abs(puts.all[[i]]$strike_price[puts.all[[i]]$date.strike == first.date & puts.all[[i]]$date.exp == last.date] - strike.ideal))
  option.id = puts.all[[i]]$optionid[puts.all[[i]]$date.strike == first.date & puts.all[[i]]$date.exp == last.date][rownum]
  
  #Take this offer price; for now, pretend like there is unlimited liquidity for this particular contract (build in a liquidity premium for now, though)
  price.contract = puts.all[[i]]$best_offer[puts.all[[i]]$optionid == option.id & puts.all[[i]]$date.strike == first.date]*liq.prem
  num.contract = floor(budget/price.contract)
  
  #Now, find the average offer price for puts sold on the day closest to 12/21/96 at the same strike price
  contracts = puts.all[[i]][puts.all[[i]]$optionid == option.id & puts.all[[i]]$date.exp == last.date,]
  price.end = contracts$best_offer[dim(contracts)[1]]
  abs.return = (price.end-price.contract)*num.contract
  returns[i] = abs.return
}
```

**Returns based on VIX index.**

```{r}
#Libraries
library(lubridate)

#Vectors to store data
option.return = rep(NA,range)
spy.return = rep(NA,range)
portfolio.return = rep(NA,range)
port.val = rep(NA,range)
spy.val = rep(NA,range)
  
#Initial values
portfolio.value = 10000
equity.value = 10000
option.perc = 0.03
equity.perc = 0.97
option.budget = portfolio.value*option.perc
equity.budget = portfolio.value*equity.perc
liq.prem = 1
vix.units = 4

#Loop through years
for(i in 1:(range-1)){
  #Determine average offer price for puts sold on in the beginning of the year and expiring at the end of the year for a strike price trading at a certain number of VIX units (in %) below the SPY level
  first.date = puts.all[[i]]$date.strike[which.min(abs(as.Date(paste(years[i],"-01-01",sep=""))-puts.all[[i]]$date.strike))]
  puts.first = puts.all[[i]][puts.all[[i]]$date.strike == first.date,]
  last.date = puts.first$date.exp[which.min(abs(as.Date(paste(years[i]+2,"-01-01",sep=""))-puts.first$date.exp))]
  
  first.weekday = as.integer(format(first.date,'%u'))
  last.weekday = as.integer(format(last.date,'%u'))
  
  first.date.equities = as.Date(ifelse(first.weekday >= 6, first.date + 4 - first.weekday, first.date))
  last.date.equities = as.Date(ifelse(last.weekday >= 6, last.date + 4 - last.weekday, last.date))
  
  #Date correction
  if(last.date.equities == "2021-12-31"){
    last.date.equities = "2021-12-30"
  }
  
  spy.init = mean(prices$SPY.Open[prices$date == first.date.equities],prices$SPY.Close[prices$date == first.date.equities],na.rm=T)*10
  vix.init = mean(prices$VIX.Open[prices$date == first.date],prices$VIX.Close[prices$date == first.date],na.rm=T)
  strike.ideal = spy.init*(1-vix.init*vix.units/100)
  
  #Option Contract ID of the historical put option which traded closest to the ideal strike price for our transaction
  rownum = which.min(abs(puts.all[[i]]$strike_price[puts.all[[i]]$date.strike == first.date & puts.all[[i]]$date.exp == last.date] - strike.ideal))
  option.id = puts.all[[i]]$optionid[puts.all[[i]]$date.strike == first.date & puts.all[[i]]$date.exp == last.date][rownum]
  
  #Take this offer price; build in a liquidity premium (liq.prem)
  price.contract = puts.all[[i]]$best_offer[puts.all[[i]]$optionid == option.id & puts.all[[i]]$date.strike == first.date]*liq.prem
  num.contract = floor(option.budget/price.contract)
  
  #Now, find the average offer price for puts sold on the day closest to 1/1/97 at the same strike price
  puts.limited = puts.all[[i]][puts.all[[i]]$optionid == option.id,]
  rebalance.date = puts.limited$date.strike[which.min(abs(as.Date(paste(years[i]+1,"-01-01",sep=""))-puts.limited$date.strike))]

  contracts = puts.all[[i]][puts.all[[i]]$optionid == option.id & puts.all[[i]]$date.strike == rebalance.date,]
  price.end = contracts$best_offer[dim(contracts)[1]]
  abs.return = (price.end-price.contract)*num.contract
  
  #Save data
  option.return[i] = abs.return/option.budget
  spy.return[i] = prices$SPY.Close[prices$date == last.date.equities]/prices$SPY.Open[prices$date == first.date.equities]-1
  
  #Update portfolio and budget data
  portfolio.return[i] = (option.budget*(1+option.return[i])+equity.budget*(1+spy.return[i]))/portfolio.value-1
  
  #Rebalance budgets for options and equities
  portfolio.value = option.budget*(1+option.return[i])+equity.budget*(1+spy.return[i])
  equity.budget = portfolio.value*equity.perc
  option.budget = portfolio.value*option.perc
  
  port.val[i] = portfolio.value
  spy.val[i] = equity.value*(1+spy.return[i])
  equity.value = spy.val[i]
}

#Chart
plot(years,spy.val,type="l")
lines(years,port.val,col="blue")
```

**Returns based on absolute % deviation from S&P level. (works best)**

```{r}
#Libraries
library(lubridate)
library(birk)

#Vectors to store data
option.return = rep(NA,range)
spy.return = rep(NA,range)
portfolio.return = rep(NA,range)
port.val = rep(NA,range)
spy.val = rep(NA,range)
  
#Initial values
portfolio.value = 10000
equity.value = 10000
option.perc = 0.08
equity.perc = 0.92
option.budget = portfolio.value*option.perc
equity.budget = portfolio.value*equity.perc
liq.prem = 1.2
spy.dev = 0.6

#Storage for graphs
put.graphs = list()

#Loop through years
for(i in 1:23){
  port.val[i] = portfolio.value
  spy.val[i] = equity.value
  
  if(i==23){
    break
  }
  
  #Determine average offer price for puts sold on in the beginning of the year and expiring at the end of the year for a strike price trading at a certain number of VIX units (in %) below the SPY level
  first.date = puts.all[[i]]$date.strike[which.min(abs(as.Date(paste(years[i+1],"-01-01",sep=""))-puts.all[[i]]$date.strike))]
  puts.first = puts.all[[i]][puts.all[[i]]$date.strike == first.date,]
  last.date = puts.first$date.exp[which.min(abs(as.Date(paste(years[i+1]+2,"-01-01",sep=""))-puts.first$date.exp))]
  
  first.weekday = as.integer(format(first.date,'%u'))
  first.date.equities = as.Date(ifelse(first.weekday >= 6, first.date + 4 - first.weekday, first.date))
  
  if(i == 1){
    spy.init = prices$SPY.Adjusted[1]*10
    vix.init = prices$VIX.Adjusted[1]
  }
  else{
    spy.init = prices$SPY.Adjusted[prices$date == first.date.equities]*10
    vix.init = prices$VIX.Adjusted[prices$date == first.date.equities]
  }
  
  strike.ideal = spy.init*(1-spy.dev)
  
  #Option Contract ID of the historical put option which traded closest to the ideal strike price for our transaction
  rownum = which.min(abs(puts.all[[i]]$strike_price[puts.all[[i]]$date.strike == first.date & puts.all[[i]]$date.exp == last.date] - strike.ideal))
  option.id = puts.all[[i]]$optionid[puts.all[[i]]$date.strike == first.date & puts.all[[i]]$date.exp == last.date][rownum]
  
  #Take this offer price; build in a liquidity premium (liq.prem)
  price.contract = puts.all[[i]]$best_offer[puts.all[[i]]$optionid == option.id & puts.all[[i]]$date.strike == first.date]*liq.prem
  num.contract = floor(option.budget/price.contract)
  
  #Now, find the average offer price for puts sold on the day closest to 1/1/97 at the same strike price
  puts.limited = puts.all[[i]][puts.all[[i]]$optionid == option.id,]
  rebalance.date = puts.limited$date.strike[which.min(abs(as.Date(paste(years[i+1]+1,"-01-01",sep=""))-puts.limited$date.strike))]
  
  #Time manipulation
  rebalance.weekday = as.integer(format(rebalance.date,'%u'))
  
  last.date.equities = as.Date(ifelse(rebalance.weekday >= 6, rebalance.date + 4 - rebalance.weekday, rebalance.date))
  

  #Date correction
  if(last.date.equities == "2021-12-31"){
    last.date.equities = "2021-12-30"
  }
  
  #Contracts
  contracts = puts.all[[i]][puts.all[[i]]$optionid == option.id & puts.all[[i]]$date.strike == rebalance.date,]
  price.end = contracts$best_offer[dim(contracts)[1]]
  abs.return = (price.end-price.contract)*num.contract

  #Save data
  option.return[i] = abs.return/option.budget
  
  if(i == 1){
    spy.return[i] = prices$SPY.Adjusted[254]/prices$SPY.Adjusted[1]-1
  }
  else{
    spy.return[i] = prices$SPY.Adjusted[prices$date == last.date.equities]/prices$SPY.Adjusted[prices$date == first.date.equities]-1
  }
  
  #Update portfolio and budget data
  portfolio.return[i] = (option.budget*(1+option.return[i])+equity.budget*(1+spy.return[i]))/portfolio.value-1
  
  #Rebalance budgets for options and equities
  portfolio.value = option.budget*(1+option.return[i])+equity.budget*(1+spy.return[i])
  equity.value = equity.value*(1+spy.return[i])
  equity.budget = portfolio.value*equity.perc
  option.budget = portfolio.value*option.perc
  
  #Save data for put graphs 
  temp = puts.all[[i]][puts.all[[i]]$optionid == option.id,]
  temp = data.frame(as.Date(temp$date.strike),temp$best_offer)
  prices.temp = data.frame(as.Date(prices$date),prices$VIX.Close)
  colnames(temp) = c("date.strike","best_offer")
  colnames(prices.temp) = c("date","vix")
  temp = merge(temp,prices.temp,by.x="date.strike",by.y="date")
  put.graphs[[i]] = temp
}

#Chart
plot(years,spy.val,type="l",main="Value of $10,000 Invested in SPY vs. Tail Risk Strategy 1, 2000-2021",xlab="Years",ylab="Value of Initial $10,000 Investment")
lines(years,port.val,col="blue")
legend(x=2000,y=40000,legend = c("SPY","Tail Risk 1"),col=c("black","blue"),lty=1,cex=0.8)

#Graphs of Option Prices vs. VIX before rebalancing
library(ggplot2)
for(i in 1:range){
  ggplot(put.graphs[[i]], aes(x=date.strike)) +
    geom_line(aes(y=best_offer)) + 
    geom_line(aes(y=vix),color="blue") + 
    scale_y_continuous(
      name = "Option Offer Price",
      sec.axis = sec_axis(~.,name="VIX")
    )
}

#Insights: the failure of the put option strategy in 2001 is largely due to timing issues. Try buying protection when VIX < 0.20289 (long-term average); exit at one of two points - if VIX is 2 standard deviations over the long-term average (37.08493 or higher; std.dev of 8.397901); or if the year ends before that. Obviously, you have to cycle through daily values, but you can just use the strike dates in the option table for your particular option ID (which introduces the prospect of missing certain days when VIX is 2 standard deviations over or below 20...but just try it for now).
#Calculate rolling 5-year returns

#Calculate yearly returns
yearlyreturns = rep(NA,(range-1))
for(i in 1:(range-1)){
  yearlyreturns[i+1]=port.val[i+1]/port.val[i]-1
}

spyyearlyreturns = rep(NA,(range-1))
for(i in 1:(range-1)){
  spyyearlyreturns[i+1]=spy.val[i+1]/spy.val[i]-1
}


fiveyear.return = rep(NA,length(yearlyreturns)-5)
fiveyear.spy.return = rep(NA,length(yearlyreturns)-5)
for(i in 2:(length(yearlyreturns)-4)){
  fiveyear.return[i] = ((1+yearlyreturns[i])*(1+yearlyreturns[i+1])*(1+yearlyreturns[i+2])*(1+yearlyreturns[i+3])*(1+yearlyreturns[i+4]))^(1/5)-1
  fiveyear.spy.return[i] = ((1+spyyearlyreturns[i])*(1+spyyearlyreturns[i+1])*(1+spyyearlyreturns[i+2])*(1+spyyearlyreturns[i+3])*(1+spyyearlyreturns[i+4]))^(1/5)-1
}

#Calculate rolling 10-year returns
tenyear.return = rep(NA,length(yearlyreturns)-10)
tenyear.spy.return = rep(NA,length(yearlyreturns)-10)
for(i in 2:(length(yearlyreturns)-9)){
  tenyear.return[i] = ((1+yearlyreturns[i])*(1+yearlyreturns[i+1])*(1+yearlyreturns[i+2])*(1+yearlyreturns[i+3])*(1+yearlyreturns[i+4])*(1+yearlyreturns[i+5])*(1+yearlyreturns[i+6])*(1+yearlyreturns[i+7])*(1+yearlyreturns[i+8])*(1+yearlyreturns[i+9]))^(1/10)-1
  tenyear.spy.return[i] = ((1+spyyearlyreturns[i])*(1+spyyearlyreturns[i+1])*(1+spyyearlyreturns[i+2])*(1+spyyearlyreturns[i+3])*(1+spyyearlyreturns[i+4])*(1+spyyearlyreturns[i+5])*(1+spyyearlyreturns[i+6])*(1+spyyearlyreturns[i+7])*(1+spyyearlyreturns[i+8])*(1+spyyearlyreturns[i+9]))^(1/10)-1
}

fiveyear.return1 = fiveyear.return
tenyear.return1 = tenyear.return
```

**Timing with VIX.**

```{r}
#Libraries
library(lubridate)
library(birk)

#Vectors to store data
option.return = rep(NA,range)
spy.return = rep(NA,range)
portfolio.return = rep(NA,range)
port.val = rep(NA,range)
spy.val = rep(NA,range)
  
#Initial values
portfolio.value = 10000
equity.value = 10000
option.perc = 0.08
equity.perc = 1-option.perc
option.budget = portfolio.value*option.perc
equity.budget = portfolio.value*equity.perc
liq.prem = 1.2
spy.dev = 0.6

prices$year = substr(prices$date,1,4)

#VIX Values
vix.mean = mean(prices$VIX.Close,na.rm=T)
vix.sdev = sd(prices$VIX.Close,na.rm=T)
vix.lower = 20
vix.upper = 70

strikes = c()
strikes.real = c()
currs = c()

#Loop through years
for(i in 1:23){
  spy.val[i] = equity.value
  port.val[i] = portfolio.value
  
  if(i == 23){
    break
  }
  
  puts.yearly = puts.all[[i]]
  vix.yearly = prices[prices$year == years[i+1],]
  num.contract = 0
  price.contract = 0
  protection = 0
  profit = 0
  temp.option.budget = option.budget
  
  for(j in 1:dim(vix.yearly)[1]){
    #If we lose all of our money for portfolio protection, don't invest anymore
    
    
    if(vix.yearly$VIX.Close[j] < vix.lower & protection == 0 & temp.option.budget > 0){
      #Take on protection (search for options with strike date on or closest after this date that are closest to 60% OTM)
      #First, tabulate options with strike price closest to 60% OTM
      spy.current = vix.yearly$SPY.Close[j]*10
      strike.ideal = spy.current*(1-spy.dev)
      
      #Find puts which traded on this day
      first.date = puts.yearly$date.strike[which.min(abs(as.Date(vix.yearly$date[j])-puts.yearly$date.strike))]
      puts.first = puts.yearly[puts.yearly$date.strike == first.date,]
      
      #Last date is two years from now
      last.date = puts.first$date.exp[which.closest((as.Date(vix.yearly$date[j])+years(2)),puts.first$date.exp)]
      
      #Option Contract ID of the historical put option which traded closest to the ideal strike price for our transaction
      rownum = which.min(abs(puts.yearly$strike_price[puts.yearly$date.strike == first.date & puts.yearly$date.exp == last.date] - strike.ideal))
      option.id = puts.yearly$optionid[puts.yearly$date.strike == first.date & puts.yearly$date.exp == last.date][rownum]
      
      #Take this offer price; build in a liquidity premium (liq.prem)
      price.contract = puts.yearly$best_offer[puts.yearly$optionid == option.id & puts.yearly$date.strike == first.date]*liq.prem
      num.contract = floor(temp.option.budget/price.contract)
      
      strikes.real = c(strikes.real, puts.yearly$strike_price[puts.yearly$optionid == option.id & puts.yearly$date.strike == first.date])
      
      #Switch protection on
      protection = 1
      dates = c(dates,j)
      
      #Create a dataframe for the price of this option exclusively
      my.option = puts.yearly[puts.yearly$optionid == option.id & puts.yearly$date.exp == last.date,]
    }
    
    #Having taken on protection, we need to watch out for selling opportunities (earlier of 2*VIX Std. Dev movement or end of year rebalancing)
    if(vix.yearly$VIX.Close[j] > vix.upper & protection == 1 & temp.option.budget > 0){
      #Find the price of the option contract on this particular day, or nearest to the day
      #Find the nearest day 
      distance = as.Date(vix.yearly$date[j])-my.option$date.strike
      sell.date = my.option$date.strike[which.min(abs(distance))]
      
      #Look up price on the sell date
      price.sale = my.option$best_offer[my.option$date.strike == sell.date]*liq.prem
      profit = (price.sale-price.contract)*num.contract + profit
      
      profits = c(profits,profit)
      temp.option.budget = temp.option.budget + profit
      
      #Switch off protection
      protection = 0
    }
    
    #Watch out for the end of the year
    if(j == dim(vix.yearly)[1] & protection == 1 & temp.option.budget > 0){
      #Find the price of the option contract on this particular day, or nearest to the day
      #Find the nearest day 
      distance = as.Date(vix.yearly$date[j])-my.option$date.strike
      sell.date = my.option$date.strike[which.min(abs(distance))]
      
      #Look up price on the sell date
      price.sale = my.option$best_offer[my.option$date.strike == sell.date]*liq.prem
      profit = (price.sale-price.contract)*num.contract + profit
      
      profits = c(profits,profit)
      temp.option.budget = temp.option.budget + profit
      
      #Switch off protection
      protection = 0
    }
  }
  
  #Tally up the profits for the year
  spy.return = vix.yearly$SPY.Adjusted[dim(vix.yearly)[1]]/vix.yearly$SPY.Adjusted[1]-1
  equity.value = equity.value*(1+spy.return)

  equity.budget = equity.budget*(1+spy.return)
  option.return[i] = (option.budget+profit)/option.budget-1
  option.budget = option.budget+profit
  portfolio.value = equity.budget + option.budget
  
  equity.budget = portfolio.value*equity.perc
  option.budget = portfolio.value*option.perc
}

#Chart
plot(years,spy.val,type="l",main="SPY vs. Tail Risk Strategy 2 with 20% Liquidity Premium, 2000-2021",xlab="Years",ylab="Value of Initial $10,000 Investment",ylim=c(0,90000))
lines(years,port.val,col="blue")
legend(x=2000,y=40000,legend = c("SPY","Tail Risk 2"),col=c("black","blue"),lty=1,cex=0.8)

#Calculate yearly returns
yearlyreturns = rep(NA,(range))
for(i in 1:(range)){
  yearlyreturns[i+1]=port.val[i+1]/port.val[i]-1
}

spyyearlyreturns = rep(NA,(range))
for(i in 1:(range)){
  spyyearlyreturns[i+1]=spy.val[i+1]/spy.val[i]-1
}

#Calculate rolling 5-year returns
fiveyear.return = rep(NA,length(yearlyreturns)-5)
fiveyear.spy.return = rep(NA,length(yearlyreturns)-5)
for(i in 2:(length(yearlyreturns)-4)){
  fiveyear.return[i] = ((1+yearlyreturns[i])*(1+yearlyreturns[i+1])*(1+yearlyreturns[i+2])*(1+yearlyreturns[i+3])*(1+yearlyreturns[i+4]))^(1/5)-1
  fiveyear.spy.return[i] = ((1+spyyearlyreturns[i])*(1+spyyearlyreturns[i+1])*(1+spyyearlyreturns[i+2])*(1+spyyearlyreturns[i+3])*(1+spyyearlyreturns[i+4]))^(1/5)-1
}

#Calculate rolling 10-year returns
tenyear.return = rep(NA,length(yearlyreturns)-10)
tenyear.spy.return = rep(NA,length(yearlyreturns)-10)
for(i in 2:(length(yearlyreturns)-9)){
  tenyear.return[i] = ((1+yearlyreturns[i])*(1+yearlyreturns[i+1])*(1+yearlyreturns[i+2])*(1+yearlyreturns[i+3])*(1+yearlyreturns[i+4])*(1+yearlyreturns[i+5])*(1+yearlyreturns[i+6])*(1+yearlyreturns[i+7])*(1+yearlyreturns[i+8])*(1+yearlyreturns[i+9]))^(1/10)-1
  tenyear.spy.return[i] = ((1+spyyearlyreturns[i])*(1+spyyearlyreturns[i+1])*(1+spyyearlyreturns[i+2])*(1+spyyearlyreturns[i+3])*(1+spyyearlyreturns[i+4])*(1+spyyearlyreturns[i+5])*(1+spyyearlyreturns[i+6])*(1+spyyearlyreturns[i+7])*(1+spyyearlyreturns[i+8])*(1+spyyearlyreturns[i+9]))^(1/10)-1
}

quantile(yearlyreturns,na.rm=T)
quantile(spyyearlyreturns,na.rm=T)
quantile(fiveyear.return,na.rm=T)
quantile(fiveyear.spy.return,na.rm=T)
quantile(tenyear.return,na.rm=T)
quantile(tenyear.spy.return,na.rm=T)
```



